\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation

### 2018-04-27 ccs/main.tex
starting ccs repo

\documentclass[conference,compsoc]{IEEEtran}

\input{headers}
\usepackage{authblk}
\IEEEoverridecommandlockouts

\begin{document}
\title{\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{
% \IEEEauthorblockN{Nishanth Chandran \hspace{10pt} Divya Gupta  \hspace{10pt} Aseem Rastogi \hspace{10pt}  Rahul Sharma } \IEEEauthorblockA{Microsoft Research, India\hspace{10pt} Email: \{nichandr,t-digu,aseemr,rahsha,t-shtrip\}@microsoft.com}
%\and
%\IEEEauthorblockN{Shardul Tripathi }
% \IEEEauthorblockA{IIT Delhi, India}
%}
%}

\author[1]{Nishanth Chandran}
\author[1]{Divya Gupta}
\author[1]{Aseem Rastogi}
\author[1]{Rahul Sharma}
%\author[1,2]{Shardul Tripathi}
\author[2]{Shardul Tripathi%\thanks{Work done while Shardul was interning at Microsoft Research India.}
}
\affil[1]{Microsoft Research India\authorcr Email: {\{nichandr,t-digu,aseemr,rahsha\}@microsoft.com}\vspace{1.5ex}}
\affil[2]{Dept. of Computer Science and Engineering, I.I.T. Delhi, India \authorcr Email: {shardul.511@gmail.com}  \vspace{-2ex}} 
%\affil[1]{Microsoft Research India \authorcr Email: {\tt \{uid1, uid2\}@microsoft.com}\vspace{1.5ex}}
%\affil[2]{Dept. of Computer Science and Engineering, IIT Delhi, India \authorcr Email: {\tt uid3@jpl.nasa.gov} \vspace{-2ex}}

\maketitle
\vspace{-100pt}
\begin{abstract}
  %% Secure two-party computation (\mpc) allows two mutually distrusting
  %% parties to compute any function on their joint inputs, without
  %% revealing anything other than the output of the function to one
  %% another.

  %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
\mpc protocols from high-level, easy-to-write, programs.
\tool provides formal correctness and security guarantees while maintaining performance and scalability.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
Previous language frameworks, such as CBMC-GC, ObliVM, SMCL, and
Wysteria,
generate protocols that use either arithmetic or boolean
circuits exclusively. Our compiler is the first to generate protocols
that combine both arithmetic sharing and garbled circuits  for better
performance.
%We give the first compiler that generates protocols which combine both arithmetic and boolean circuits
%for better performance compared to protocols that use either arithmetic or boolean circuits exclusively.
We
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x)
recent works that provide hand-crafted protocols for various
functionalities such as secure  prediction  and matrix factorization.
%\tool provides formal correctness and security guarantees.
%% (up to
%% a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

@@

%\newpage
\bibliographystyle{abbrv}
\bibliography{bib}
%\balance

%\appendix
%\input{app-stash}

>>>>

\documentclass[sigconf, anonymous]{acmart}

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
\acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained

\input{headers}

%\usepackage{epsfig,endnotes,pdfpages}
\usepackage{wrapfig}
\usepackage{float}
\begin{document}

\title{\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation}

\begin{abstract}
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
\mpc protocols from high-level, easy-to-write, programs.
\tool provides formal correctness and security guarantees while maintaining performance and scalability.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
Previous language frameworks, such as CBMC-GC, ObliVM, SMCL, and
Wysteria,
generate protocols that use either arithmetic or boolean
circuits exclusively. Our compiler is the first to generate protocols
that combine both arithmetic sharing and garbled circuits  for better
performance.
%We give the first compiler that generates protocols which combine both arithmetic and boolean circuits
%for better performance compared to protocols that use either arithmetic or boolean circuits exclusively.
We
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x)
recent works that provide hand-crafted protocols for various
functionalities such as secure  prediction  and matrix factorization.

\end{abstract}

\setlength\intextsep{1pt}
\setlength{\textfloatsep}{1pt}
\setlength{\abovecaptionskip}{4pt}
\setlength{\belowcaptionskip}{4pt}

\maketitle

@@

%\newpage

{\footnotesize \bibliographystyle{acm}
\bibliography{bib}}

%\bibliographystyle{abbrv}
%\bibliography{bib}
%\balance

\appendix

\input{appendix_b}

\input{appendix_c}

\input{appendix_a}

### 2018-04-27 ccs/pipe.tex
starting ccs repo

\newcommand{\prog}{s}
\newcommand{\progn}{t}
\newcommand{\seq}{||}
\newcommand{\state}{q}

@@

Let $\prog$ be a program that takes (secret) inputs $x$ from Alice and
$y$ from Bob and produces an output $z$ to both parties. Let
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$ be a decomposition of $\prog$
such that the following holds. Define $\state_0 = \bot$ (the public empty
state). For all
$1\leq i\leq k-1$, $\prog_i$ takes inputs $x, y$ and $\state_{i-1}$ and
outputs state $\state_i$. Finally, $\prog_k$ takes inputs $x, y$ and
$\state_{k-1}$ to  output $z$. It is
possible to decompose any program $\prog$  into such
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$. If \tool generates circuit
$\crct_i$ from
$\prog_i$, the parties can execute
$\crct_1, \crct_2, \dots \crct_k$
sequentially (in a distributed setting)  to obtain
$\state_1,\dots,\state_{k-1},$ and finally output $z$. At the
$i^{\textrm{\tiny{th}}}$ step, the parties only need to store
information proportional to $x,y,\state_{i-1}$ and $\crct_i$ (which is
much smaller than $\crct$). However, this execution enables the
parties to learn $\state_i$ (for all $1\leq i\leq k-1$), which
completely breaks the security.

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\state_0
= \bot$. Without
loss of generality, let all $\state_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\state_0$), and runs $\prog_1$ (as defined above) to
compute $\state_1$ and then outputs $o_1 = \state_1 + r_1$ {\em only
  to} Bob\footnote{While the description of our protocol here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
  }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\state_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\state_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\state_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties.

>>>>

\newcommand{\prog}{s}
\newcommand{\progn}{t}
\newcommand{\seq}{||}
\newcommand{\stateq}{q}

@@

Let $\prog$ be a program that takes (secret) inputs $x$ from Alice and
$y$ from Bob and produces an output $z$ to both parties. Let
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$ be a decomposition of $\prog$
such that the following holds. Define $\stateq_0 = \bot$ (the public empty
state). For all
$1\leq i\leq k-1$, $\prog_i$ takes inputs $x, y$ and $\stateq_{i-1}$ and
outputs state $\stateq_i$. Finally, $\prog_k$ takes inputs $x, y$ and
$\stateq_{k-1}$ to  output $z$. It is
possible to decompose any program $\prog$  into such
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$. If \tool generates circuit
$\crct_i$ from
$\prog_i$, the parties can execute
$\crct_1, \crct_2, \dots \crct_k$
sequentially (in a distributed setting)  to obtain
$\stateq_1,\dots,\stateq_{k-1},$ and finally output $z$. At the
$i^{\textrm{\tiny{th}}}$ step, the parties only need to store
information proportional to $x,y,\stateq_{i-1}$ and $\crct_i$ (which is
much smaller than $\crct$). However, this execution enables the
parties to learn $\stateq_i$ (for all $1\leq i\leq k-1$), which
completely breaks the security.

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\stateq_0
= \bot$. Without
loss of generality, let all $\stateq_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\stateq_0$), and runs $\prog_1$ (as defined above) to
compute $\stateq_1$ and then outputs $o_1 = \stateq_1 + r_1$ {\em only
  to} Bob\footnote{While the description of our protocol here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
  }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\stateq_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\stateq_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\stateq_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties.

### 2018-04-27 ccs/related.tex
starting ccs repo

\vspace{-0.1in}
\section{Related work}
\label{sec:related}

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized, hand-crafted protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure the security of the protocols.
Examples include privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, private sequence analysis~\cite{franz}, private biometric identification~\cite{huang}, privacy-preserving matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

>>>>

\vspace{-0.2in}
\section{Related work}
\label{sec:related}

@@

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}
